### 2016-07-13 paper/extended-example.tex

\section{Extended Example}

Consider building a lens which converts between between citations given
in EndNote format, and in BibTex format.  For simplicity, we are only
considering the author and title fields.  The synthesis problem for these
two regular expressions is provided below.

\begin{figure}
\begin{lstlisting}
Name    = [A-Z][a-z]*
Initial = [A-Z] "."
Word    = ([A-Z] | [a-z] | "-" | "," | ":")+
Title   = Word (" " Word)*

FN      = Name", " Name (" " (Name | Initial))*
Type    = "@inproceedings" | "@article"
BibTex  = 
  Type "{" 
    Word ","
    ("" | ("title={" Title "},"))
    ("" | ("author={" FN (" and " FN)* "},")) 
  "}"

EName   = Name (" " (Name | Initial))* (" " Name)
Class   = "Conference Paper" | "Journal Article"
EndNote = "%0 " Class "\n"
	 ("%A " EName "\n")*
	 ("" | "%T TITLE")
	  "%1 " Word "\n"

BibEndConv : BibTex <=> EndNote = ?
\end{lstlisting}
\caption{Synthesis Problem: Simplified Bibtex to EndNote}
\end{figure}

\begin{lstlisting}
Name = [A-Z][a-z]*
Names = Name (" " Name)*

@@

BibEnd : Bib <=> End = {
"author={Conway, John and Kleene, Stephen Cole}"
<-> "%A John Conway\n%A Stephen Cole Kleene" }
\end{lstlisting}

>>>>

\section{Lens Synthesis by Example}

\dpw{the lstlisting environment is drawing a line underneath the code.
I don't want that.  we need to fix it but I'm focusing on writing.
Also, it may be good to hack it so it can be in a backslash small font.
There is perhaps another environment we could use -- a code environment.}

In order to explain the major components of our synthesis algorithm,
we will consider a running example involving conversion between citations given
in highly simplified BibTex and EndNote formats.  Our BibTex format
consists entirely of specifying a list of authors on a single line as follows.
\begin{lstlisting}
author={Conway, John and Kleene, Stephen Cole}
\end{lstlisting}
Our EndNote format contains the same information, but uses different separators,
rearranges the order of first and last names, and uses a separate line for each
author. 
\begin{lstlisting}
%A John Conway
%A Stephen Cole Kleene
\end{lstlisting}

\begin{figure}
\begin{lstlisting}
Name = [A-Z][a-z]*
Names = (" " Name)*

@@

BibEnd : Bib <=> End = {
"author={Conway, John and Kleene, Stephen Cole}"
<-> "%A John Conway\n%A Stephen Cole Kleene" }
\end{lstlisting}
\caption{Synthesis Problem Definition: Idealized Bibtex to EndNote}
\label{fig:bibend-spec}
\end{figure}

Figure~\cite{fig:bibend-spec} presents
the user's specification of such a problem.  In general, such specifications are
given by defining the source and target data formats~\footnote{Lenses
operate both left-to-right and right-to-left, so both formats are sometimes
sources and sometimes targets. Nevertheless, we will often call the
format on the left, the ``source,'' and the format on the right, 
the ``target.''} as well as some examples.  In this case, the lens
we wish to synthesize is \CF{BibEnd}.  It converts between 
the formats \CF{Bib} and \CF{End}.
Such formats are defined using a standard syntax for regular expressions.
Intermediate regular expressions are named in order to facilitate
construction of complex formats.

\subsection{Regular Bijective Lenses}

Once we have a synthesis specification, we need to find a lens that
will convert back and forth between formats and that satisfies the
given examples.  In this paper, we begin our work with a simple and 
relatively standard language of bijective string lens combinators.
In order to guarantee the functions generated by these combinators
form proper bijections between source and target, they are given types using regular expressions.  
We typicallly write 
$\Lens \OfType \Regex \Leftrightarrow \RegexAlt$ to indicate that
a lens $\Lens$ converts back and forth between data belonging
to the languages of regular expressions
$\Regex$ and $\RegexAlt$.

The simplest lens in the combinator language is the identity lens 
at type $R$,
$\IdentityLensOf{R}$, which copies data matching regular expression $R$
from source to target, and vice versa.  The
constant lens $\ConstLens{\String_1}{\String_2}$, when operated left-to-right, 
replaces string $\String_1$ with $\String_2$, and when operated right-to-left,
replaces string $\String_2$ with $\String_1$.

Each of the other lenses manipulate structured data.  For instance,
$\ConcatLens{\Lens_1}{\Lens_2}$

\paragraph*{Step 1:  Inlining Definitions.}

\dpw{----------------}
